junk_final_assignment

### 2022-11-27 draft_final_assingment.Rmd
More wordclouds

@@

#Wordcloud comparing Congress
```{r}
dfmat3 <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Congress) %>%
    dfm_trim(min_termfreq = 3)

>>>>

#Wordcloud congress 116

```{r}
dfmat4 <- dfm(corpus_subset(corp, Congress == 116), remove = stopwords("english"), remove_punct = TRUE) %>%
    dfm_trim(min_termfreq = 1)

textplot_wordcloud(dfmat4, max_words = 300)

#Wordcloud congress 117

```{r}
dfmat5 <- dfm(corpus_subset(corp, Congress == 117), remove = stopwords("english"), remove_punct = TRUE) %>%
    dfm_trim(min_termfreq = 1)

textplot_wordcloud(dfmat5, max_words = 300)

@@

#Wordcloud comparing Congresses
```{r}
dfmat3 <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Congress) %>%
    dfm_trim(min_termfreq = 3)
